---
title: "Data Cleaning for CLAHRC NWL Heart Failure Care Bundle Analysis"
author: "Dr. Thomas Woodcock"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Cleaning for CLAHRC NWL Heart Failure Care Bundle Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette covers the data cleaning process from the raw data provided by
North West London Hospitals to a clean dataset ready for analysis.

## Input
The raw data is contained in the file `/data/admission_data.rda`. This file
contains a single dataframe, admission_data, which is created from the original
raw data files in `/data-raw` by the script `/data-raw/load-raw-data.R` which
simply stitches the separate files together.

The functions required for cleaning the data are all contained within the
`data_cleaning.R` script.



## Missing Data
As part of the data extract and pseudonymisation process, missing data has been
represented as both `"NULL"` and `"#N/A"` in the raw data. The `clean_data`
function resolves both of these to `NA`, resulting in the following distribution
of missing data across columns.

```{r, echo=FALSE, results='asis'}
admission_data_clean <- clahrcnwlhf::clean_data(clahrcnwlhf::admission_data)
nac <- clahrcnwlhf::na_count(admission_data_clean)
library(knitr)
kable(nac)
```

For some fields, it is not important that there is a significant amount of
missing data; e.g. the fact that many of the secondary diagnosis fields are
missing may be entirely natural - not all episodes of care involve nine
different diagnoses!

## Vignette text example

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
