---
title: "Data Cleaning for CLAHRC NWL Heart Failure Care Bundle Analysis"
author: "Dr. Thomas Woodcock"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Cleaning for CLAHRC NWL Heart Failure Care Bundle Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette covers the data cleaning process from the raw data provided by
North West London Hospitals to a clean dataset ready for analysis.

## Input
The raw data is contained in the file `/data/admission_data.rda`. This file
contains a single dataframe, admission_data, which is created from the original
raw data files in `/data-raw` by the script `/data-raw/load-raw-data.R` which
simply stitches the separate files together.

The functions required for cleaning the data are all contained within the
`data_cleaning.R` script.

## Date formatting
All dates in the raw data are expressed as character strings starting
yyyy-mm-dd. We therefore use the regex `"^[0-9]{4}-[0-9]{2}-[0-9]{2}"`
to extract the date part of strings in the following columns of the raw data:
`AdmissionDate`, `DischargeDate`, `EpisodeStartDate`, `EpisodeEndDate`.

## Missing Data
As part of the data extract and pseudonymisation process, missing data has been
represented as both `"NULL"` and `"#N/A"` in the raw data. The `clean_data`
function resolves both of these to `NA`, resulting in the following distribution
of missing data across columns.

```{r, echo=FALSE, results='asis', cache=TRUE}
admission_data_clean <- clahrcnwlhf::clean_data(clahrcnwlhf::admission_data,
                                                restrict_disch_date = FALSE)
library(knitr)
library(scales)
nac <- clahrcnwlhf::na_count(admission_data_clean)
n <- nrow(admission_data_clean)
nact <- data.frame(nac,nac/n*100)
colnames(nact) <- c("Number_of_NAs", "Percent_NAs")
knitr::kable(nact[order(nact[,2]),])
```

For some fields, it is not important that there is a significant amount of
missing data; e.g. the fact that many of the secondary diagnosis fields are
missing may be entirely natural - not all episodes of care involve nine
different diagnoses!

To check for any patterns in missing data over time, let's look at this by year.

```{r, echo=FALSE, results='asis', cache=TRUE}
#admission_data_clean <- clahrcnwlhf::clean_data(clahrcnwlhf::admission_data,
#                                                restrict_disch_date = FALSE)
library(knitr)
library(scales)
md <- clahrcnwlhf::missing_data_table(admission_data_clean)
knitr::kable(t(md))
```

The percentage of missing data for the following fields looks higher for 2016
compared with previous years: `CSPAdmissionTime`, `CSPDischargeTime`,
`CSPLastWard`, `PrimaryDiagnosis`. Let's look at these percentages at a more
granular timescale.

```{r, fig.height=5, fig.width=7, cache=TRUE}
#admission_data_clean <- clahrcnwlhf::clean_data(clahrcnwlhf::admission_data,
#                                                restrict_disch_date = FALSE)
p <- clahrcnwlhf::missing_data_table(admission_data_clean, split_by = '%Y-%m',
                                     result = 'percent_no_total')
pmd_monthly <- p[,colnames(p) %in% c("CSPAdmissionTime","CSPDischargeTime",
                                     "PrimaryDiagnosis","CSPLastWard")]
matplot(pmd_monthly, type = c("b"),pch=1:4,col = 1:4, xaxt="n")
axis(side=1,at=1:nrow(pmd_monthly),labels=rownames(pmd_monthly), las = 2, cex.axis =0.6)
legend("topleft", legend = colnames(pmd_monthly), col=1:4, pch=1:4)
```

This shows two things:

1. The proportion of missing data in the `PrimaryDiagnosis` field goes up dramatically for episodes with DischargeDate in the last two months of data (October and November 2016)
2. The proportions of missing data in the fields `CSPAdmissionTime`, `CSPDischargeTime`, `CSPLastWard`, go up by an order of magnitude for episodes with DischargeDate in the last seven months of data (May - November 2016).

The increase in missing `PrimaryDiagnosis` values in the last two months (1) is
likely to be a result of the usual delay in coding. Therefore these months
will not be used in the analysis.

The missing data in the fields `CSPAdmissionTime`, `CSPDischargeTime`,
`CSPLastWard` is not so easily explained, and Steve Hiles from North West
London Hospitals is investigating this at present (25th November 2016).

For now, let's look at the new missing data summary excluding those last two
months:


```{r, echo=FALSE, results='asis',cache=TRUE}
#admission_data_clean <- clahrcnwlhf::clean_data(clahrcnwlhf::admission_data,
#                                                restrict_disch_date = TRUE)
library(knitr)
library(scales)
nac <- clahrcnwlhf::na_count(admission_data_clean)
n <- nrow(admission_data_clean)
nact <- data.frame(nac,nac/n*100)
colnames(nact) <- c("Number_of_NAs", "Percent_NAs")
knitr::kable(nact[order(nact[,2]),])
```


---






## Vignette text example

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
