---
title: "Descriptive Analysis for CLAHRC NWL Heart Failure Care Bundle: 2 - Demographics"
author: "Dr. Thomas Woodcock"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


This vignette covers the descriptive data analysis of demographics for the
evaluation of the CLAHRC NWL Heart Failure Care Bundle project at North West London Hospitals.

## Ethnicity - all NPH discharges

```{r, echo=TRUE, results='asis', cache=TRUE}
library(knitr)
emergency_adms <- clahrcnwlhf::emergency_adms
emergency_spells <- emergency_adms[
  which(emergency_adms[,"EpisodeNumber"] == 1),]
emergency_spells_nph <- emergency_spells[which(emergency_spells[,"StartWardSite"] == "NPH"),]
knitr::kable(t(as.data.frame.table(table(emergency_spells_nph$EthnicGroup))))
```

The overall proportions in each ethnic group show that the groups within the
category "Mixed" (D - G) account for a very small proportion of spells. Thus it
makes sense to combine them into a single new group, X. Group K (Bangladeshi)
also represents a very small proportion of spells, and will be merged with Group
L (Any other Asian background) to form a new group I. Codes M, N, P  will be
treated as their category, Black or Black British, labelled U. Chinese (R) is a
small group and will be merged with the other group in its category
(S, any other ethnic group) to form group V.


```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_spells_nph$EthnicGroupComp <- sub('D|E|F|G','T',emergency_spells_nph$EthnicGroup)
emergency_spells_nph$EthnicGroupComp <- sub('K|L','I',emergency_spells_nph$EthnicGroupComp)
emergency_spells_nph$EthnicGroupComp <- sub('M|N|P','U',emergency_spells_nph$EthnicGroupComp)
emergency_spells_nph$EthnicGroupComp <- sub('R|S','V',emergency_spells_nph$EthnicGroupComp)
knitr::kable(t(as.data.frame.table(table(emergency_spells_nph$EthnicGroupComp))))
```

First let us examine the number of discharges each month by ethnic group.

```{r, fig.height=5, fig.width=7, echo=TRUE, results='asis', cache=TRUE}
library(ggplot2, reshape2)

X <- clahrcnwlhf::ethn_time_table(emergency_spells_nph, ethn_col = 'EthnicGroupComp')
Y <- as.data.frame.matrix(t(X))
Y$timepoint <- c(1:58)
Y.melted <- reshape2::melt(Y, id = "timepoint")
ggplot(data = Y.melted, aes(x = timepoint, y = value, color = variable)) + geom_point() + geom_line()


```

Next, we consider this data as a proportion of all discharges.

```{r, fig.height=5, fig.width=7, echo=TRUE, results='asis', cache=TRUE}
Y <- as.data.frame.matrix(t(X))
n <- ncol(Y)
Y$total <- rowSums(Y)
Y[,1:n] <- Y[,1:n] / Y[,n+1]
Z <- Y
Y$total <- NULL
Y$timepoint <- c(1:58)
Y.melted <- reshape2::melt(Y, id = "timepoint")
ggplot(data = Y.melted, aes(x = timepoint, y = value, color = variable)) + geom_point() + geom_line()

```

We now consider the distribution of ethnicity between the two time periods.

```{r, echo=TRUE, results='asis', cache=TRUE}
library(pander, descr)
emergency_spells_nph <- clahrcnwlhf::group_by_date(emergency_spells_nph, cutoff_dates = c(as.Date("31/12/2011", "%d/%m/%Y"),as.Date("31/03/2014", "%d/%m/%Y"),as.Date("30/11/2016", "%d/%m/%Y")), period_labels = c('Before', 'After'), new_col = 'period')
Table1 <- descr::CrossTable(emergency_spells_nph$EthnicGroupComp, emergency_spells_nph$period, expected = FALSE, prop.r = FALSE, prop.t = FALSE, prop.chisq = TRUE, chisq = TRUE)
Table1$RowData <- 'Ethnicity Group'
Table1$ColData <- 'Period'
pander(Table1)
pander(Table1$CST)
```

This shows that there is a statistically significant difference between the ethnicity distributions of all NPH spells across the two periods. 

## Ethnicity - primary diagnosis heart failure

Now let us repeat the above for only those spells with primary diagnosis heart failure.

```{r, echo=TRUE, results='asis', cache=TRUE}
knitr::kable(t(as.data.frame.table(table(emergency_spells_nph[emergency_spells_nph$Heart.Failure.Episode == TRUE,]$EthnicGroupComp))))
```

Let us examine the number of primary coded heart failure discharges each month by ethnic group.

```{r, fig.height=5, fig.width=7, echo=TRUE, results='asis', cache=TRUE}

X <- clahrcnwlhf::ethn_time_table(emergency_spells_nph[emergency_spells_nph$Heart.Failure.Episode == TRUE,], ethn_col = 'EthnicGroupComp')
Y <- as.data.frame.matrix(t(X))
Y$timepoint <- c(1:nrow(Y))
Y.melted <- reshape2::melt(Y, id = "timepoint")
ggplot(data = Y.melted, aes(x = timepoint, y = value, color = variable)) + geom_point() + geom_line()


```

Next, we consider this data as a proportion of all primary coded heart failure discharges.

```{r, fig.height=5, fig.width=7, echo=TRUE, results='asis', cache=TRUE}
Y <- as.data.frame.matrix(t(X))
n <- ncol(Y)
Y$total <- rowSums(Y)
Y[,1:n] <- Y[,1:n] / Y[,n+1]
Z <- Y
Y$total <- NULL
Y$timepoint <- c(1:nrow(Y))
Y.melted <- reshape2::melt(Y, id = "timepoint")
ggplot(data = Y.melted, aes(x = timepoint, y = value, color = variable)) + geom_point() + geom_line()

```

We now consider the distribution of ethnicity between the two time periods.

```{r, echo=TRUE, results='asis', cache=TRUE}
library(pander, descr)
Table1 <- descr::CrossTable(emergency_spells_nph[emergency_spells_nph$Heart.Failure.Episode == TRUE,"EthnicGroupComp"], emergency_spells_nph[emergency_spells_nph$Heart.Failure.Episode == TRUE,"period"], expected = FALSE, prop.r = FALSE, prop.t = FALSE, prop.chisq = TRUE, chisq = TRUE)
Table1$RowData <- 'Ethnicity Group'
Table1$ColData <- 'Period'
pander(Table1)
pander(Table1$CST)
```

This shows that there is a statistically significant difference between the ethnicity distributions of spells primary coded heart failure, across the two periods. 
