---
title: "Descriptive Analysis for CLAHRC NWL Heart Failure Care Bundle: 1 - Admissions"
author: "Dr. Thomas Woodcock"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette covers the descriptive data analysis of admission numbers for the evaluation of the
CLAHRC NWL Heart Failure Care Bundle project at North West London Hospitals.

This assumes the `clahrcnwlhf::admission_data` data has been cleaned using `clahrcnwlhf::clean_and_save`. As of 18th December 2016 this includes all
discharges from 1st January 2012 to 31st October 2016 inclusive.

## Dataset

We will focus on emergency admissions data; in other words those episodes
for which 'admission_data_clean$AdmissionType = "Emergency"'. Let us first
restrict the dataset to only these episodes.

```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_adms <- clahrcnwlhf::admission_data_clean[
  which(clahrcnwlhf::admission_data_clean[,"AdmissionType"] == "Emergency"),]

```

This leaves us with `r nrow(emergency_adms)` emergency episodes with discharge
date between 1st January 2012 and 30th September 2016 inclusive. Flag columns
have been added to identify those episodes and spells with a primary diagnosis
of heart failure, and with any diagnosis of heart failure. A spell number
variable has also been added, to identify which episodes are part of the same
spell. 

```{r, echo=TRUE, results='asis', cache=TRUE}
#emergency_adms <- clahrcnwlhf::new.pat(emergency_adms, id = "PseudoID",
#                                         adt = "CSPAdmissionTime")
#emergency_adms <- clahrcnwlhf::new_spell(emergency_adms)

#emergency_adms <- clahrcnwlhf::make.spellnumber.2(emergency_adms)

#The function make.spellnumber.2 takes some time to run. To save time, load this
#dataset in directly. All previous operations in this vignette have been
#performed on this saved dataset by clahrcnwlhf::make_emergency_adms_dataset
emergency_adms <- clahrcnwlhf::emergency_adms

```



## Number of Discharges by Month

Let us first restrict attention to only the first episode of each spell.

```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_spells <- emergency_adms[
  which(emergency_adms[,"EpisodeNumber"] == 1),]

```

This gives `r nrow(emergency_spells)` discharges between 1st January 2012 and
31st October 2016 inclusive. Let us see how these vary by month over this
period.

First we look at all discharges from the three sites combined.

```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch <- clahrcnwlhf::disch_time_table(emergency_spells)
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,6500),
        main="Total emergency discharges from NWLH by month")
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```

Now let us examine the monthly number of discharges by site.

```{r, echo=TRUE, results='asis', fig.height=5, fig.width=7, cache=TRUE}
em_sp_site <- split(emergency_spells, emergency_spells$StartWardSite)
ndisch_site <- lapply(em_sp_site, clahrcnwlhf::disch_time_table)
site_names <- names(ndisch_site)
X <- cbind(ndisch_site[[1]], ndisch_site[[2]][match(labels(ndisch_site[[1]]), labels(ndisch_site[[2]]))])
site_disch <- cbind(X, ndisch_site[[3]][match(row.names(X), labels(ndisch_site[[3]]))])
colnames(site_disch) <- site_names
matplot(site_disch[,1], type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,6500),
        main="Total emergency discharges from NWLH by month and site")
matplot(site_disch[,2], type = c("b"), pch=19, col = 1, xaxt="n", ylim=c(0,6500), add=TRUE)
matplot(site_disch[,3], type = c("b"), pch=18, col = 1, xaxt="n", ylim=c(0,6500), add=TRUE)
axis(side=1,at=1:nrow(site_disch),labels=row.names(site_disch), las = 2, cex.axis =0.6)
legend("topright", inset=.05, legend=site_names, pch=c(20,19,18), col = 1, horiz=TRUE)
```


We now restrict attention to spells commencing on the Northwick Park site only.
```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_adms <- emergency_adms[which(emergency_adms[,"StartWardSite"] == "NPH"),]
emergency_spells <- emergency_adms[
  which(emergency_adms[,"EpisodeNumber"] == 1),]

```

This results in `r max(emergency_adms$spell_number)` emergency spells at NPH
with discharge date between 1st January 2012 and 30th September 2016 inclusive.


```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch <- clahrcnwlhf::disch_time_table(emergency_spells)
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,6500),
        main="Total emergency discharges from Northwick Park Hospital by month")
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```


Next let's look at this for those spells with primary diagnosis code
heart failure.

```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch_hf <- clahrcnwlhf::disch_time_table(emergency_spells[
  which(emergency_spells[,"Heart.Failure.Episode"] == TRUE),])
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch_hf, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,100),
        main="Monthly discharges primary diagnosis Heart Failure, NPH")
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```

There are a total of `r sum(n_disch)` spells with primary diagnosis code
heart failure for the period. 

Now let us look at the *proportion* of discharges with primary diagnosis heart failure.

```{r, fig.height=5, fig.width=7, cache=TRUE}

p_disch_hf <- n_disch_hf / n_disch
#n_disch <- n_disch[-length(n_disch)]

hf_proportion_data <- cbind(n_disch, n_disch_hf, p_disch_hf)
#knitr::kable(hf_proportion_data)

matplot(p_disch_hf, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,0.04),
        main="Primary diag. HF discharges as proportion of all emergency discharges, NPH")
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```

We can examine this data for evidence of change after the date the project commenced, namely 1st April 2014, using a p-chart.

```{r, fig.height=5, fig.width=7, cache=TRUE}
library(qcc)
pcc1 <- qcc(data = hf_proportion_data[1:match("2014-03",rownames(hf_proportion_data)),"n_disch_hf"], sizes = hf_proportion_data[1:match("2014-03",rownames(hf_proportion_data)),"n_disch"], plot = FALSE, type = "p", newdata = hf_proportion_data[match("2014-04",rownames(hf_proportion_data)):nrow(hf_proportion_data),"n_disch_hf"], newsizes = hf_proportion_data[match("2014-04",rownames(hf_proportion_data)):nrow(hf_proportion_data),"n_disch"], chart.all = TRUE, data.name = "period before project start")
pcc1$newdata.name <- "period after project start"
plot(pcc1, title = "Proportion of emergency admissions discharged with primary diag. heart failure", xlab = "Month", ylab = "Proportion of heart failure discharges", yaxt="n")
axis(2, at=pretty(c(pcc1$statistics,pcc1$newstats)), lab = paste(pretty(c(pcc1$statistics,pcc1$newstats)) * 100, "%"), las=TRUE)


```


## Other diagnosis positions

We will now look at discharge numbers for patients with a diagnosis code in
positions other than Primary Diagnosis.

```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch <- clahrcnwlhf::disch_time_table(emergency_spells[
  which(emergency_spells[,"HF.any.code"] == TRUE),])
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,400),
        main="Monthly discharges any diagnosis HF, NPH")
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```








