---
title: "Descriptive Analysis for CLAHRC NWL Heart Failure Care Bundle: 4 - Data Linkage"
author: "Dr. Thomas Woodcock"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette covers the data linkage results for the evaluation of the
CLAHRC NWL Heart Failure Care Bundle project at North West London Hospitals.

## Linking process and exploratory analysis

Description of process here. Include removal of duplicated bundle links.

## Linking results

```{r, echo=FALSE, results='asis', cache=TRUE}

library(scales)

linked_bundle_data <- clahrcnwlhf::linked_bundle_data
linked_nicor_data <- clahrcnwlhf::linked_nicor_data

N_bundles <- nrow(clahrcnwlhf::bundle_data_clean)
n_bundles_linked <- nrow(linked_bundle_data[!is.na(linked_bundle_data$linked.spell),])

N_nicor <- nrow(clahrcnwlhf::nicor_data_clean)
n_nicor_linked <- nrow(linked_nicor_data[!is.na(linked_nicor_data$linked.spell),])

```

Of the `r N_bundles` care bundle records, `r n_bundles_linked` (`r percent(n_bundles_linked / N_bundles)`) were linked to an emergency admission spell, leaving `r N_bundles - n_bundles_linked` (`r percent( 1- n_bundles_linked / N_bundles )`) remaining unlinked (or duplicates of better links).

Of the `r N_nicor` nicor records, `r n_nicor_linked` (`r percent(n_nicor_linked / N_nicor)`) were linked to an emergency admission spell, leaving `r N_nicor - n_nicor_linked` (`r percent( 1- n_nicor_linked / N_nicor )`) remaining unlinked.

These results are summarised by the following Venn Diagram showing how many emergency
admission spells are linked to bundles, nicor records, or both.

```{r, echo=TRUE, results='asis', cache=TRUE, fig.height=4, fig.width=6,}

clahrcnwlhf::plot_linking_venn(episodes = clahrcnwlhf::emergency_adms, linked_bundles = linked_bundle_data, linked_nicor = linked_nicor_data)

```

Looking only at emergency admissions coded with primary diagnosis Heart Failure,
the picture is the following:

```{r, echo=TRUE, results='asis', cache=TRUE, fig.height=4, fig.width=6,}

clahrcnwlhf::plot_linking_venn(episodes = clahrcnwlhf::emergency_adms[which(clahrcnwlhf::emergency_adms$Heart.Failure.Episode == TRUE),], linked_bundles = linked_bundle_data, linked_nicor = linked_nicor_data)

```

Finally looking at emergency admissions coded with heart failure in any diagnosis
position:

```{r, echo=TRUE, results='asis', cache=TRUE, fig.height=4, fig.width=6,}

clahrcnwlhf::plot_linking_venn(episodes = clahrcnwlhf::emergency_adms[which(clahrcnwlhf::emergency_adms$HF.any.code == TRUE),], linked_bundles = linked_bundle_data, linked_nicor = linked_nicor_data)

```

Note that in the all of the above diagrams, only the `r n_bundles_linked` linked bundles and the `r n_nicor_linked` linked nicor records, are included.
