---
title: "Descriptive Analysis for CLAHRC NWL Heart Failure Care Bundle"
author: "Dr. Thomas Woodcock"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette covers the descriptive data analysis for the evaluation of the
CLAHRC NWL Heart Failure Care Bundle project at North West London Hospitals.

This assumes the `clahrcnwlhf::admission_data` data has been cleaned using `clahrcnwlhf::clean_and_save`. As of 1st December 2016 this includes all
discharges after 1st January 2012 and 30th September 2016 inclusive.

## Dataset

This part of the analysis will focus on emergency admissions data; in other
words those episodes for which
'admission_data_clean$AdmissionType = "Emergency"'. Let us first restrict the
dataset to only these episodes

```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_adms <- clahrcnwlhf::admission_data_clean[
  which(clahrcnwlhf::admission_data_clean[,"AdmissionType"] == "Emergency"),]

```

This leaves us with `r nrow(emergency_adms)` emergency episodes with discharge
date between 1st January 2012 and 30th September 2016 inclusive. We will need to
identify those episodes and spells with a primary diagnosis of heart failure,
and with any diagnosis of heart failure so let us add flag columns to indicate
such episodes.

```{r, echo=TRUE, results='asis', cache=TRUE}
#emergency_adms <- clahrcnwlhf::make_diag_flag(emergency_adms,
#                                   code_regex="I110|I255|I420|I429|I500|I501|I509",
#                                   new_colname = "Heart.Failure.Episode")
#emergency_adms <- clahrcnwlhf::make_anydiag_flag(emergency_adms, "Diagnosis", "HF.any.code", #"I110|I255|I420|I429|I500|I501|I509")

```

We will need a spell number variable, to identify which episodes are part of the
same spell. The following code creates this column, along with some helper
columns.

```{r, echo=TRUE, results='asis', cache=TRUE}
#emergency_adms <- clahrcnwlhf::new.pat(emergency_adms, id = "PseudoID",
#                                         adt = "CSPAdmissionTime")
#emergency_adms <- clahrcnwlhf::new_spell(emergency_adms)

#emergency_adms <- clahrcnwlhf::make.spellnumber.2(emergency_adms)

#The function make.spellnumber.2 takes some time to run. To save time, load this
#dataset in directly. All previous operations in this vignette have been
#performed on this saved dataset by clahrcnwlhf::make_emergency_adms_dataset
emergency_adms <- clahrcnwlhf::emergency_adms

```



## Number of Discharges by Month

Let us first restrict attention to only the first episode of each spell.

```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_spells <- emergency_adms[
  which(emergency_adms[,"EpisodeNumber"] == 1),]

```

This gives `r nrow(emergency_spells)` discharges between 1st January 2012 and
30th September 2016 inclusive. Let us see how these vary by month over this
period.

First we look at all discharges from the three sites combined.

```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch <- clahrcnwlhf::disch_time_table(emergency_spells)
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,6500))
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```

Now let us examine the monthly number of discharges by site.

```{r, echo=TRUE, results='asis', fig.height=5, fig.width=7, cache=TRUE}
em_sp_site <- split(emergency_spells, emergency_spells$StartWardSite)
ndisch_site <- lapply(em_sp_site, clahrcnwlhf::disch_time_table)
site_names <- names(ndisch_site)
X <- cbind(ndisch_site[[1]], ndisch_site[[2]][match(labels(ndisch_site[[1]]), labels(ndisch_site[[2]]))])
site_disch <- cbind(X, ndisch_site[[3]][match(row.names(X), labels(ndisch_site[[3]]))])
colnames(site_disch) <- site_names
matplot(site_disch[,1], type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,6500))
matplot(site_disch[,2], type = c("b"), pch=19, col = 1, xaxt="n", ylim=c(0,6500), add=TRUE)
matplot(site_disch[,3], type = c("b"), pch=18, col = 1, xaxt="n", ylim=c(0,6500), add=TRUE)
axis(side=1,at=1:nrow(site_disch),labels=row.names(site_disch), las = 2, cex.axis =0.6)
legend("topright", inset=.05, legend=site_names, pch=c(20,19,18), col = 1, horiz=TRUE)
```


We restrict attention to spells commencing on the Northwick Park site only.
```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_adms <- emergency_adms[which(emergency_adms[,"StartWardSite"] == "NPH"),]
emergency_spells <- emergency_adms[
  which(emergency_adms[,"EpisodeNumber"] == 1),]

```

This results in `r max(emergency_adms$spell_number)` emergency spells with
discharge date between 1st January 2012 and 30th September 2016 inclusive.


```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch <- clahrcnwlhf::disch_time_table(emergency_spells)
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,6500))
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```


Next let's look at this for those spells with primary diagnosis code
heart failure.

```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch_hf <- clahrcnwlhf::disch_time_table(emergency_spells[
  which(emergency_spells[,"Heart.Failure.Episode"] == TRUE),])
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch_hf, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,100))
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```

There are a total of `r sum(n_disch)` spells with primary diagnosis code
heart failure for the period. 

Now let us look at the proportion of discharges with primary diagnosis heart failure.

```{r, fig.height=5, fig.width=7, cache=TRUE}

p_disch_hf <- n_disch_hf / n_disch
#n_disch <- n_disch[-length(n_disch)]

matplot(p_disch_hf, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,0.04))
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```

## Other diagnosis positions

We will now look at admission numbers for patients with a diagnosis code in positions
other than Primary Diagnosis.

```{r, fig.height=5, fig.width=7, cache=TRUE}

n_disch <- clahrcnwlhf::disch_time_table(emergency_spells[
  which(emergency_spells[,"HF.any.code"] == TRUE),])
#n_disch <- n_disch[-length(n_disch)]

matplot(n_disch, type = c("b"), pch=20, col = 1, xaxt="n", ylim=c(0,400))
axis(side=1,at=1:length(n_disch),labels=names(n_disch), las = 2, cex.axis =0.6)
```








