---
title: "Descriptive analysis for age band distribution for CLAHRC NWL Heart Failure Care Bundle"
author: "Dr . Mable Nakubulwa"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Descriptive analysis for age band distribution for CLAHRC NWL Heart Failure Care Bundle}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette is a description of the distribution characteristics of patients' Age bands for the CLAHRC NWL Heart Failure Care Bundle project at North West London Hospitals.

The original raw data set from North West London Hospitals `clahrcnwlf::admission_data` was extracted and cleaned for analysis by Dr. T Woodcock using `clahrcnwlhf::clean_and_save`. The data covers discharge periods 1st January 2012 to 31st October 2016.

## Data set
This analysis is restricted to only emergency admissions data `clahrcnwlhf::emergency_adms` (i.e. data for those episodes for which `admission_data_clean$AdmissionType = "Emergency"`).


```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_adms <- clahrcnwlhf::admission_data_clean[
  which(clahrcnwlhf::admission_data_clean[,"AdmissionType"] == "Emergency"),]

```


```

#Notes needed here

```{r, echo=TRUE, results='asis', cache=TRUE}

emergency_adms <- clahrcnwlhf::emergency_adms

```


AGE DISTRIBUTION FREQUENCY

Let us first restrict attention to only the first episode of each spell.

```{r, echo=TRUE, results='asis', cache=TRUE}
emergency_spells <- emergency_adms[
  which(emergency_adms[,"EpisodeNumber"] == 1),]

```

## Age band distribution (split by) `period.date`

First lets plot a plot of age-dist `Age Band` frequency using `emergency_spells data`. Age Band in the first ggplot is  split by `period.date`: period `A` (discharges before the CLAHRC NWL Heart Failure Care Bundle project) and period `B` (discharges after the CLAHRC NWL Heart Failure Care Bundle project)

```{r, fig.height=5, fig.width=7, cache=TRUE}
#test <- clahrcnwlhf::plot_age_dist(emergency_adms)
#dataframe restricted to only rows where 'new.spell' = TRUE
ggplot2::ggplot(emergency_adms, ggplot2::aes(x=AgeBand))+ggplot2::geom_bar(width= 0.7)+ggplot2::facet_wrap( ~ period.date)+ggplot2::ggtitle("Distribution by Age Band Across Period Dates A and B")+ggplot2::coord_flip()+ggplot2::ylab("Frequency")+ggplot2::xlab("Age Band")
```


## Age band distribution (Overall distribution, i.e period.date A & B combined)
Second lets plot out 

```{r, fig.height=5, fig.width=7, cache=TRUE}
ggplot2::ggplot(emergency_adms, ggplot2::aes(x=AgeBand))+ggplot2::geom_bar(width= 0.7)+ggplot2::ggtitle("Distribution by Age Bands")+ggplot2::coord_flip()+ggplot2::ylab("Frequency")+ggplot2::xlab("Age Band")

```

## Frequency table

```{r, fig.height=5, fig.width=7, cache=TRUE}

ageband_perioddate <- clahrcnwlhf::plot_dist_table(emergency_adms)
#age band distribution for both periods + sum of both
addmargins(table(emergency_adms$AgeBand, emergency_adms$period.date),2)
ageband_perioddate #this is what I run in the command line

```




The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
