---
title: 'Reproducible Research'
author: 'Tom Woodcock'
date: "`r Sys.Date()`"
output:
  beamer_presentation:
    toc: true
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
min_date_cutoff <- as.Date('2012-01-01')
max_date_cutoff <- as.Date('2017-07-31')
```

# Introduction: Reproducible Research

## The problem

```{r}
img1_path <- "Reproducible-research-files/Repr_Res_Problem_1.png"
knitr::include_graphics(img1_path)
```

## The problem

```{r}
img2_path <- "Reproducible-research-files/Repr_Res_Problem_2.png"
knitr::include_graphics(img2_path)
```

## What is reproducible research?

> The goal of reproducible research is to tie specific instructions to data analysis and experimental data so that scholarship can be recreated, better understood and verified.

[https://CRAN.R-project.org/view=ReproducibleResearch](https://CRAN.R-project.org/view=ReproducibleResearch)

## How does it work?

```{r}
img3_path <- "Reproducible-research-files/Repr_Res_Workflow_1.png"
knitr::include_graphics(img3_path)
```

## How does it work?

```{r}
img4_path <- "Reproducible-research-files/Repr_Res_Workflow_2.png"
knitr::include_graphics(img4_path)
```

## Why reproducible research in CLAHRC NWL?
Reproducible research has the potential to

- Increase transparency of analysis and methods

- Facilitate repeat analysis by our team

- Enable analysis to be reproduced by other researchers
    - to verify results and understand what was done
    - to conduct analogous research in their setting
- Enable analysis to be reproduced by other improvers
    - to understand what data may be needed to replicate an initiative
    - to adopt operational definitions
    - to analyse their own data to drive improvement and evaluate
- Facilitate aggregation of results from multiple sites implementing interventions with a common 'core'



<!-- # Example 1: Unscheduled Care Flow -->

```{r ae-example, child = 'AE-example-1.Rmd'}
```

```{r hf-example, child = 'HF-example-1.Rmd'}
```


# Next steps and discussion

## Next steps and discussion

Heart Failure

- publish Northwest London Hospitals analysis

- apply reproducible analysis in roll-out within NWL (++)
 
Unscheduled Care

- develop apps and analyses - UEC collaborative

- publication(s)

- approach NHS England?
 
 Capability Building
 
- Coding Club!

- Recruitment/secondments
 
 Future

- Publish on the approach in improvement science

- CLAHRC projects using routine data - use reproducible research

- Explore collaborations nationally (and internationally)
